Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-04 pecomplexity.tex
finish off the table of results

\begin{table}[htdp]
\caption{Average nRMSE over 15 runs for each signal and average (?) pe [[Ryan:is this average over all 15 and is this weighted]] at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Horizon&nRMSE LMA & nRMSE mean & $l=5$& $l=6$\\
\hline
gcc &4542&  $0.1407\pm0.0063 $   & $0.1487\pm0.0066$ & - & - \\
col\_major &14,709&  $0.0252\pm0.0061$   & $0.1975\pm0.0436$ & - & -\\

SVD\_Full &22,072&  $0.0323\pm0.0019$  & $ 0.1784\pm0.0040$ & - & -  \\
SVD\_IPC\_Regime1 &2,158&  $0.1680 \pm 0.0317$  & $0.3517\pm0.5223$ &0.9786 &0.9675  \\
SVD\_IPC\_Regime2 &6,902& $0.1716 \pm0.0043 $  &$0.1762 \pm0.0012$ &0.8800&0.8493 \\
SVD\_IPC\_Regime3 &947& $0.0507 \pm 0.0011$   &$0.5413\pm0.0005$  &0.7646&0.7029\\
SVD\_IPC\_Regime4 &2,929&  $0.1288\pm0.0471$  & $0.2308\pm0.0867$ &0.8735&0.7770\\
SVD\_IPC\_Regime5 &3,255&  $0.0235\pm0.0022$ & $0.1306\pm0.0003$&0.7281&0.6724 \\
SVD\_IPC\_Regime6 &5,804&  $0.0196\pm0.0022$  & $0.0508\pm0.0003$ &0.8316&0.7615 \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

>>>>

\begin{table}[htdp]
\caption{Average nRMSE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                  & Horizon & nRMSE LMA           & nRMSE mean          & $l=5$                   & $l=6$                   \\
\hline
gcc               & 4,542   & $0.1407 \pm 0.0063$ & $0.1487 \pm 0.0066$ & $0.950991 \pm 0.001073$ & $0.942964 \pm 0.001256$ \\

col\_major        & 14,709  & $0.0252 \pm 0.0061$ & $0.1975 \pm 0.0436$ & $0.563640 \pm 0.003110$ & $0.513101 \pm 0.003365$ \\

SVD\_Full         & 22,072  & $0.0323 \pm 0.0019$ & $0.1784 \pm 0.0040$ & $0.876517 \pm 0.004354$ & $0.850805 \pm 0.003454$ \\
SVD\_IPC\_Regime1 & 2,158   & $0.1680 \pm 0.0317$ & $0.3517 \pm 0.5223$ & $0.976109 \pm 0.008359$ & $0.957204 \pm 0.015623$ \\
SVD\_IPC\_Regime2 & 6,902   & $0.1716 \pm 0.0043$ & $0.1762 \pm 0.0012$ & $0.875984 \pm 0.005161$ & $0.846360 \pm 0.004420$ \\
SVD\_IPC\_Regime3 & 947     & $0.0507 \pm 0.0011$ & $0.5413 \pm 0.0005$ & $0.776841 \pm 0.007290$ & $0.715747 \pm 0.005605$ \\
SVD\_IPC\_Regime4 & 2,929   & $0.1288 \pm 0.0471$ & $0.2308 \pm 0.0867$ & $0.907348 \pm 0.008018$ & $0.824626 \pm 0.007707$ \\
SVD\_IPC\_Regime5 & 3,255   & $0.0235 \pm 0.0022$ & $0.1306 \pm 0.0003$ & $0.733272 \pm 0.007562$ & $0.677575 \pm 0.006792$ \\
SVD\_IPC\_Regime6 & 5,804   & $0.0196 \pm 0.0022$ & $0.0508 \pm 0.0003$ & $0.810087 \pm 0.013468$ & $0.747545 \pm 0.010607$ \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%
